Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}

### 2017-02-14 hscc2017/paper.tex
nudge

Beyond classical a-posteriori validation procedures in digital control,
there has been plenty of previous work aiming at \emph{verifying} a given 
designed controller, which however broadly lack automation.  
Recent work has studied the stability of digital controllers with consideration of their implementation aspects, i.e.,
fixed-point arithmetic and the word length used: 
\cite{Bessa16} exploit advances in bit-accurate verification of C
programs to obtain a verifier for software-implemented digital control.

By contrast, we leverage a very recent step-change in the automation and scalability of 
\emph{program synthesis}.  Program synthesis engines use a program
specification as the starting point, and subsequently generate a sequence of
candidate programs from a given template.  
The candidate programs are iteratively refined to eventually match the desired program specification.   
Program synthesizers implementing the 
Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{sketch} architecture are now
able to generate programs for highly non-trivial specifications with a very 
high degree of automation.  Modern synthesis engines combine automated testing, 
genetic algorithms, 
and SMT-based automated reasoning~\cite{DBLP:journals/corr/AlurFSS16a,DBLP:conf/lpar/DavidKL15}.

@@

Our work addresses challenging aspects of the control synthesis problem.  We
perform digital control synthesis over a hybrid model, where the plant
exhibits continuous behavior whereas the controller operates in discrete
time and over a quantized domain.  Inspired by a classical
approach~\cite{astrom1997computer}, we translate the problem into a single
digital domain.  
Towards our goal of closed-loop stability, 
% despite digitization effects, 
we have modeled a digital equivalent of the continuous plant by evaluating the effects of the quantizers (A/D and D/A converters) and of time
discretization. 
% elements with quantization noise.  
We further account for uncertainties on the plant models. 
The resulting closed-loop system is a program loop that operates on bit-vectors encoded using
fixed-point arithmetic with finite word length (FWL).  
The three effects of 1. uncertaities, 2. FWL representation, and 3. quantization errors are incorporated into the model, 
%as an additive uncertainty, 
and are taken into account during the CEGIS-based synthesis of the control software for the plant.

>>>>

Beyond classical a-posteriori validation procedures in digital control,
there has been plenty of previous work aiming at \emph{verifying} a given
designed controller, which however broadly lack automation.  Recent work has
studied the stability of digital controllers considering implementation
aspects, i.e., fixed-point arithmetic and the word length~\cite{Bessa16}. 
They exploit advances in bit-accurate verification of C programs to obtain a
verifier for software-implemented digital control.

By contrast, we leverage a very recent step-change in the automation and
scalability of \emph{program synthesis}.  Program synthesis engines use a
specification as the starting point, and subsequently generate a sequence of
candidate programs from a given template.  The candidate programs are
iteratively refined to eventually satisfy the specification.  Program
synthesizers implementing Counter-Example Guided Inductive Synthesis
(CEGIS)~\cite{sketch} are now able to generate programs for highly
non-trivial specifications with a very high degree of automation.  Modern
synthesis engines combine automated testing, genetic algorithms, and
SMT-based automated reasoning~\cite{DBLP:journals/corr/AlurFSS16a,
DBLP:conf/lpar/DavidKL15}.

@@

Our work addresses challenging aspects of the control synthesis problem.  We
perform digital control synthesis over a hybrid model, where the plant
exhibits continuous behavior whereas the controller operates in discrete
time and over a quantized domain.  Inspired by a classical
approach~\cite{astrom1997computer}, we translate the problem into a single
digital domain.  
Towards our goal of closed-loop stability, 
% despite digitization effects, 
we have modeled a digital equivalent of the continuous plant by evaluating the effects of the quantizers (A/D and D/A converters) and of time
discretization. 
% elements with quantization noise.  
%
We further account for uncertainties on the plant models.  The resulting
closed-loop system is a program loop that operates on bit-vectors encoded
using fixed-point arithmetic with finite word length (FWL).  The three
effects of 1.~uncertaities, 2.~FWL representation and 3.~quantization
errors are incorporated into the model,
%
%as an additive uncertainty, 
and are taken into account during the CEGIS-based synthesis of the control software for the plant.
